\hypertarget{omri-nisan-solan---cv}{%
\section{\texorpdfstring{\textbf{Omri Nisan Solan -
CV}}{Omri Nisan Solan - CV}}\label{omri-nisan-solan---cv}}

I am a Bourgain Fellow and an associate research scholar at Princeton
University and at the Institute of Advanced Study.

\hypertarget{education}{%
\subsection{\texorpdfstring{\textbf{Education:}}{Education:}}\label{education}}

\begin{itemize}
\item
  2010 - 2015: Bachelor of Science, Mathematics, Tel Aviv University
  (Summa cum laude).
\item
  2015 - 2021: Master student at Tel Aviv university, under the
  supervision of Prof.~Barak Weiss (Summa cum laude).
\item
  2022 - 2025: Ph.D.~student at the Hebrew University of Jerusalem,
  under the supervision of Prof.~Elon Lindenstrauss.
\item
  2025 - 2029: Bourgain Fellow and an associate research scholar at
  Princeton University and at the Institute of Advanced Study.
\end{itemize}

\hypertarget{research-interest}{%
\subsection{\texorpdfstring{\textbf{Research
Interest:}}{Research Interest:}}\label{research-interest}}

My primary research focus is on homogeneous dynamics. I leverage tools
from number theory, probability, and algebraic topology to address
problems in this field.

\hypertarget{teaching}{%
\subsection{\texorpdfstring{\textbf{Teaching:}}{Teaching:}}\label{teaching}}

\begin{itemize}
\item
  2023 - Teaching assistant, Hebrew University of Jerusalem, the course
  ``Fundamental concepts in spectral analysis''.
\item
  2024 - Teaching assistant, Hebrew University of Jerusalem, the course
  ``Fundamental concepts in commutative algebra and algebraic
  geometry''.
\end{itemize}

\hypertarget{awards}{%
\subsection{\texorpdfstring{\textbf{Awards:}}{Awards:}}\label{awards}}

\begin{itemize}
\item
  International Mathematical Olympiad, 2012 silver medal, 2013 gold
  medal, 2014 silver medal.
\item
  International Mathematics Competition for University Students, 2014,
  First Prize, 2015 Grand First Prize \& Prize for special solution,
  2017 First Prize.
\item
  Dean's award for distinguished students - Tel Aviv University
  (2015).
\item
  Award of excellence for Master's Studies Tel Aviv University (2021).
\item
  `Lior Tzafriri' Award for excellence in Ph.D.~studies.
\end{itemize}

\hypertarget{active-participation-in-scientific-meetings}{%
\subsection{\texorpdfstring{\textbf{Active Participation in Scientific
Meetings:}}{Active Participation in Scientific Meetings:}}\label{active-participation-in-scientific-meetings}}

\begin{itemize}
\item
  2015 - ``Divergent Trajectories in SL3(R)/SL3(Z)'', Dynamics \&
  Probability - Hebrew University of Jerusalem, Israel.
\item
  2017 - ``Stable and Well-Rounded Lattices in Diagonal Orbits'' -
  Action Now Wandering Seminar, Ben Gurion University, Israel.
\item
  2021 - ``Parametric Geometry of Numbers with General Flows'',
  Diophantine Analysis and Related Topics, online conference.
\item
  2021 - ``Geometry of the Casp and Divergent Trajectories'', Dynamics
  \& Probability - Hebrew University of Jerusalem, Israel.
\item
  2022 - ``Algebraic Divergence and Geometry of Symmetric Spaces'',
  Groups \& Dynamics Seminar - Tel Aviv University, Israel.
\item
  2023 -- ``Limits of Compact Diagonal Orbits in the Lattice Space'',
  `Diophantine Analysis, Dynamics and Related Topics' conference -
  Technion, Israel.
\item
  2024 - ``Divergence of large dimensional diagonal orbits'', `Diagonal
  actions in the space of lattices' workshop - Ecole Polytechnique,
  Palaiseau, France.
\item
  2024 - ``Gap in critical exponents of SL2($\mathbb{R}$) orbits in nonarithmetic
  quotients of SL2($\mathbb{C}$)'', `Group Actions with Hyperbolicity and Measure
  Rigidity' workshop - Institut Henri Poincare, Paris, France.
\item
  2024 - ``Gap in critical exponents of SL2($\mathbb{R}$) orbits in nonarithmetic
  quotients of SL2($\mathbb{C}$)'', `Distribution of orbits: Arithmetics and
  Dynamics' workshop - Paxmontana Switzerland.
\item
  2024 - ``Gap in critical exponents'', `Recent Trends in Homogeneous
  and Teichmuller Dynamics' workshop - Maryland.
\item
  2024 - ``Gap in critical exponents'', Dynamical Systems Seminar - Penn
  State University.
\item
  2024 - ``Gap in critical exponents'', Group Actions, Geometry and
  Dynamics - Yale University.
\item
  2024 - ``Gap in critical exponents'', Joint IAS/PU Groups and Dynamics
  Seminar.
\item
  2024 - ``Limits of compact diagonal orbits in the lattice space'',
  `Dynamics and Number Theory' workshop - Hebrew University of
  Jerusalem, Israel.
\item
  2025 - ``Returns in flat surface dynamics'', Tzafriri Talk - Hebrew
  University of Jerusalem, Israel.
\item
  2025 - ``Critical exponent gap in hyperbolic geometry'', UC San Diego
  Group Actions Seminar.
\item
  2025 - ``Gap in critical exponents'', `The Ergodic Method in Group
  Theory' conference - Northwestern University.
\item
  2025 - ``Random walk on homogeneous spaces'', Midrasha on Groups -
  Weizmann Institute of Science, Israel.
\item
  2025- ``Random walks on the space of lattices'', Mathematics
  Colloquium - Tel-Aviv University, Israel.
\item
  2025 - ``Random walk on homogeneous spaces'', Groups \& Dynamics -
  Hebrew University of Jerusalem, Israel.
\item
  2026 - ``Equidistribution of expanding horospheres in the space of
  translation surfaces'' - Joint IAS/PU Groups and Dynamics Seminar.
\end{itemize}

\hypertarget{service-to-the-community}{%
\subsection{\texorpdfstring{\textbf{Service to the
Community:}}{Service to the Community:}}\label{service-to-the-community}}

\begin{itemize}
\item
  2015-2017 - Trainer in the Israeli Mathematical Olympiad Program.
\item
  2019-2021 - Private tutoring of the Mathematical Olympiad.
\end{itemize}
